Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-17 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:17	10:54:49	(Mon17.Aug)

\subsection{Beamforming}

@@

A beamformer is a spatial filter we apply to backscattered wavefield data to perform e.g. source localization and amplitude estimation. In sonar image reconstruction we desire

>>>>

\subsection{Receive Beamforming}

@@

To form a sonar image we need to estimate source locations and amplitudes. For this purpose we apply a spatial bandpass filter to the backscattered wavefield data, commonly called a receive beamformer.
